\LARGE \bf WORKING TITLE: Incorporating User Feedback in Motion Planning for Manipulators

### 2014-09-29 paper2015asml.tex
new pictures, text
added some refs and more text to online survey process

\usepackage{amsmath}
\usepackage{cases}
\usepackage{xspace}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

@@

The surveys were presented to users of Amazon Mechanical Turk, who would be presented with a set of demographic questions, a video, and the four scales to rate the robot's motion on the basis of elegance, efficency, smoothness and overall impression. Additionally a control question was presented with another video asking the participant about the robot's action in the accompanying video. This served as the first satisficing trap to ensure that participants were truthfully attempting the survey. On overview of the main survey question can be seen in Figure~\ref{fig:survey_question}.

@@

\todo Write demographic questions and compensation

\todo Write about survey participants

\todo Write about control question

\todo Write about satisficing control and concerns

>>>>

\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{cases}
\usepackage{xspace}
%\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

@@

@@

\subsubsection{Demographic Questions}

Participants were asked a few demographic questions which ask about:

\begin{itemize}
\item Familiarity with videogames
\item Familiarity with robotics
\item The participant's age group: We asked whether the participant belonged to the 18-24, 25-44, 45-64, and 65+ age brackets.
\item The participant's highest education level: We asked if the particpant had a PhD/Masters, a Bachelors, Associate or High School level degree as their highest education.
\end{itemize}

None of these pieces of information were used to filter the responses we collected.

\todo find info on relation between videogame and robotics

\subsubsection{Survey Design and Process}

The surveys were presented to users of Amazon Mechanical Turk~\cite{paolacci2010running}, who would be presented with a set of demographic questions, a video, and the four scales to rate the robot's motion on the basis of elegance, efficency, smoothness and overall impression. Additionally a control question was presented with another video asking the participant about the robot's action in the accompanying video. This served as the first satisficing trap to ensure that participants were truthfully attempting the survey. On overview of the main survey question can be seen in Figure~\ref{fig:survey_question}.

Mechanical Turk allows dispensing of monetary compensation on completion, which was set to 15\textcent~ per survey. The expected time to complete was 1-2 minutes, which allows the participant about 1 whole minute of deliberation when assigning ratings. Additionally, the participants were allowed to replay the trajectory video repeatedly (and other features that Youtube supports). This maximum possible payout is 15.45\textdollar~ or if each survey took on average 1.5 minutes to complete about 6\textdollar~ per hour of work for a participant.

\begin{figure}
\includegraphics[trim = 0mm 0mm 0mm 0mm, width=\columnwidth]{pictures/amazon_control_question}
\caption{The survey control question which prompts the participant about the action of the robot in the accompanying video. The question we adopted was to ask the particpant which colored cube the robot touched.}
\label{fig:control_question}
\end{figure}

In addition to the rating and demographic questions, a control question was incorporated to account for satisficing in online surveys~\cite{krosnick1991response}~\cite{krosnick1996satisficing}. The question format can be seen in Figure~\ref{fig:control_question}. This question served as the first counter-measure against satisficing in the survey. The other counter-measure was to manually inspect the responses, and assess whether it agrees with the other survey respondents on a participant-by-participant and then trajectory-by-trajectory basis. The process for examining a particular participant involves seeing how his/her ratings agree or disagree with the average ratings of all the other ratings for this particular trajectory. Aggregating this over all the trajectories the participant rated gives us an idea of how much we can trust their responses and make a decision about rejecting all or none of their responses. Another heuristic we employed in inspecting the responses was looking for the average time to complete the survey to be extremely low, which could hint at strong satisficing.
